### 2018-12-22 Sections/quantum_algorithms.tex
BS verification

The algorithms described previously are examples of \textit{decision problems}\index{Decision problems}, whereby the computation answers a question, providing a well-defined output for a well-defined input. Another entirely different class of problems are the so-called \textit{sampling problems}, whereby the goal is to accurately reproduce samples taken from some probability distribution. By their nature, these algorithms are statistical and generally their output cannot be associated with the answer to a decision problem. Nonetheless, despite being an entirely different category of problems, such problems reside in distinct sampling complexity classes, some of which are classically efficient to simulate, others not.

@@

>>>>

The algorithms described previously are examples of \textit{decision problems}\index{Decision problems}, whereby the computation answers a question, providing a well-defined output for a well-defined input. Another entirely different class of problems are the so-called \textit{sampling problems}, whereby the goal is to accurately reproduce samples taken from some probability distribution. By their nature, these algorithms are statistical and generally their output cannot be associated with the answer to a decision problem. Nonetheless, despite being an entirely different category of problems, they reside in distinct sampling complexity classes, some of which are classically efficient to simulate, others not.

@@

In computationally hard sampling problems, e.g quantum ones, the goal is generally not to reconstruct the complete probability distribution. This is generally impossible in the quantum context, since the number of basis states we are sampling from is exponentially large, and therefore cannot be efficiently fully reconstructed. Thus the goal of \textit{sampling} is distinct from the goal of \textit{reconstruction}. In the case of sampling problems, we are satisfied with incomplete data, provided that we only have to take a polynomial number of samples for the sake of computational efficiency.

However, this limitation to having incomplete data makes the problem of verification\index{Verification} a conceptually challenging one. We are unable to simply compare our statistical results with that of a reliable reference, since our massively incomplete samples are almost certainly going to be entirely different ones, providing no benchmark for comparison. Therefore verification by comparison is effectively ruled out, requiring more elaborate verification techniques, something which has become a highly active area of research on its own. Addressing the verification problem is of course an important one -- when we reach the milestone of achieving `quantum supremacy'\index{Quantum supremacy}, we'd sure like to be able to convincingly prove to the world that we in fact did!
